Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-06-08 manuscript.tex
'the p-value' instead of 'the one' [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/462370801e58f3852f21ccde9145286c09202383.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/462370801e58f3852f21ccde9145286c09202383/checks
https://github.com/habi/acinar-analysis-manuscript/runs/919037910

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...504f52655e0083208065c208367146913c6c4b95}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/504f52655e0083208065c208367146913c6c4b95/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/504f52655e0083208065c208367146913c6c4b95}{habi/acinar-analysis-manuscript@504f526}
on June 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(504f526)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(504f526)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\begin{figure}
\hypertarget{fig:02}{%
\centering
\includegraphics{images/fig02.png}
\caption{Distribution of the number of alveoli per acinus (entrance ring count per acinus) for each animal.
Left: linear scale, right: logarithmic scale.
The entrance ring counts per day are all significantly different (all p-values smaller than 1.9e-5, which is the one between days 4 and 10).}\label{fig:02}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:03}{%
\centering
\includegraphics{images/fig03.png}
\caption{Distribution of the acinar volumes for each animal.
Left: linear scale, right: logarithmic scale.
The acinar volumes are all significantly different (all p-values smaller than 4.5e-6, which is the one between days 10 and 21) for each combination of days except between days 4 and 10 (p=0.08).}\label{fig:03}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics{images/fig05.png}
\caption{Number of alveoli per acinus volume.
Left: linear scale, right: logarithmic scale.
The number of alveoli per acinus volume are all significantly different (all p-values are smaller than 5e-5, which is the one between days 4 and 21) for each combination of days except between days 10 and 21 (p=0.7).}\label{fig:05}
}
\end{figure}

The counts per volume, which correspond to the number of alveoli per acinus volume are one of several measure for influencing the complexity of the single acini.
The number of alveoli per acinus show highly significant differences between all possible combinations of days except between days 10 and 21 (p=0.7).
All other days have a p-value smaller than 5e-5, this being the one between days 4 and 21.
The statistical analysis is equal to what is briefly described for the entrance ring count above.
The counts per volume for all animals except 04A are non-normally distributed, but all are independent (p=2.9e-21).

@@

Multi-breath gas-washout is also dependent on the size of the acini.
Based on computational simulations of nitrogen multi-breath gas-washout it has been shown that small acini washout faster at the beginning and slower at the end of the washout as compared to larger acini {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}.
Not surprisingly, the distribution of the acinar sizes also also an influence on the gas-washout.
Furthermore, a clustering versus an even distribution of the locations of similar acinar sizes also affects gas-washout.
Therefore, the question where an acinus of which size is located in the lungs has a significant influence on pulmonary ventilation and particle deposition.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...462370801e58f3852f21ccde9145286c09202383}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/462370801e58f3852f21ccde9145286c09202383/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/462370801e58f3852f21ccde9145286c09202383}{habi/acinar-analysis-manuscript@4623708}
on June 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(4623708)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(4623708)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

\begin{figure}
\hypertarget{fig:02}{%
\centering
\includegraphics{images/fig02.png}
\caption{Distribution of the number of alveoli per acinus (entrance ring count per acinus) for each animal.
Left: linear scale, right: logarithmic scale.
The entrance ring counts per day are all significantly different (all p-values smaller than 1.9e-5, which is the p-value between days 4 and 10).}\label{fig:02}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:03}{%
\centering
\includegraphics{images/fig03.png}
\caption{Distribution of the acinar volumes for each animal.
Left: linear scale, right: logarithmic scale.
The acinar volumes are all significantly different (all p-values smaller than 4.5e-6, which is the p-value between days 10 and 21) for each combination of days except between days 4 and 10 (p=0.08).}\label{fig:03}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics{images/fig05.png}
\caption{Number of alveoli per acinus volume.
Left: linear scale, right: logarithmic scale.
The number of alveoli per acinus volume are all significantly different (all p-values are smaller than 5e-5, which is the p-value between days 4 and 21) for each combination of days except between days 10 and 21 (p=0.7).}\label{fig:05}
}
\end{figure}

The counts per volume, which correspond to the number of alveoli per acinus volume are one of several measure for influencing the complexity of the single acini.
The number of alveoli per acinus show highly significant differences between all possible combinations of days except between days 10 and 21 (p=0.7).
All other days have a p-value smaller than 5e-5, this being the p-value between days 4 and 21.
The statistical analysis is equal to what is briefly described for the entrance ring count above.
The counts per volume for all animals except 04A are non-normally distributed, but all are independent (p=2.9e-21).

@@

Multi-breath gas-washout is also dependent on the size of the acini.
Based on computational simulations of nitrogen multi-breath gas-washout it has been shown that small acini washout faster at the beginning and slower at the end of the washout as compared to larger acini {[}\protect\hyperlink{ref-eb0gk6VO}{13}{]}.
Not surprisingly, the distribution of the acinar sizes also has an influence on the gas-washout.
Furthermore, a clustering versus an even distribution of the locations of similar acinar sizes also affects gas-washout.
Therefore, the question where an acinus of which size is located in the lungs has a significant influence on pulmonary ventilation and particle deposition.
